---
title: "Jacquelyn Fusco"
author: "Politicial scientist seeking \n an administrative role doing a public service \n in the nonprofit sector"
date: "10/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
library(tidyverse)
```

```{r}
name = "Jacquelyn Fusco"
desc = "Politicial scientist seeking \n an administrative role doing a public service \n in the nonprofit sector"
cell = "(516) 456-2946"
email = "jacquelynjoan@gmail.com"
address = "439 West Olive Street \n Long Beach, NY 11561"
header = tibble(
  about = c(name, desc, address),
  contact = c("", cell, email)
)
```

```{r, fig.width = 12}
header %>% 
  knitr::kable(col.names = c("",""), format = "markdown", padding = 2)
```


|         |              |
| ------  | ------------ |
| cell    |$~~$ (516) 456-2946 |
| email   |$~~$ jacquelynjoan@gmail.com |
| address |$~~$ 439 West Olive Street, Long Beach, NY 11561 |
| LinkedIn |$~~$ https://www.linkedin.com/in/jacquelynjoan

***

## Experience

***
### Northwell Health, Lake Success, NY

#### September 2018 - present

##### Human Resources Call Center Customer Service Specialist

Explained benefits to 12,000 employees via online chats and answering phones.

Traced 1,500 missing paychecks by interviewing HR representatives to diagnose the problem.

Interpreted 5,000 payroll discrepancies by counselling the employee how to resolve the issue.

***

#### May 2018 - August 2018

##### Donor Acknowledgement Operations Specialist

Drafted and proofread 1,000 thank you letters using Lexis Nexis and Raiser’s Edge to double-check details including name, title, and the reason for the donation reducing mistakes by 99%.

Communicated tax acknowledgment query results to team members daily.

***

#### October 2017 - May 2018

##### Data Management Donations Operations Specialist

Reported up to 100 fundraising donations per day for 27 hospitals using Raiser’s Edge.

Researched checks to extract donor details daily for reports in Raiser’s Edge.

***

#### March 2017 - October 2017

##### Clinical Data Management Operations Specialist

Coordinated with 20 healthcare practices to transfer healthcare information to a database using Excel.

Taught providers to complete forms and update biweekly checklists to maintain incentive eligibility.

***

#### January 2017 - March 2017

##### Talent Acquisition Onboarding Specialist

Facilitated the onboarding of over 400 new employees by organizing resumes and background checks.

***

## Activities

***

### Nassau County Democratic Socialists of America

#### July 2019 - June 2020

##### Grassroots Organization Executive Secretary

Wrote email campaigns to direct members to attend events and reported minutes at meetings monthly.

Redesigned cloud management of the communication systems, including shared documents, event details and volunteer lists to improve social media reach by 300%.

***

### Sunrise Movement, Long Island, NY				  	  	 

#### March 2018 - January 2020

##### Founder, Sunrise Hub Coordinator

Recruited 5 young people to persuade state representatives and elected officials to support climate justice legislation to reduce greenhouse gases 100% by 2030.

Recommended 200 people to vote for a climate champion in a local election.

***

### Long Island Progressive Coalition, Massapequa, NY	        	        	        

#### October 2017 - December 2019

##### Environmental Community Organizer Volunteer

Liaised with 20 people from community organizations across Long Island to support climate action in New York. 

Led a workshop about intersectionality in the climate movement at a climate summit held in Brentwood, NY to educate 50 people.

***

## Education

***

### Baruch College School of Public Affairs, New York, NY

#### Master of Public Administration (M.P.A.), concentration in Nonprofit Management

Thesis: “The Importance of Cultural Change and the Dangers in Dismissing It”

***

### Long Island University, C.W. Post Campus, Brookville, NY

#### Bachelor of Arts (B.A.) in Political Science

Minor in Sociology